What is the impact of weather catastrophe frequency and severity on property insurance policy prices, and how can homeowners alleviate financial strain?

### 2023-10-30 manuscript/manuscript.tex
added refs and discussion

\section{Data}
\label{sec:data}
To comprehend the impact of weather-related catastrophic events on property insurance pricing, we will begin by examining a dataset of 
billion-dollar disasters. This dataset provides crucial information on event frequency, financial cost, and other key parameters. Our 
data sources include the National Centers for Environmental Information (NCEI)\cite{ncei}, the Insurance Information Institute 
(III)\cite{iii}, Aon\cite{aon} and the National Association of Insurance Commissioners (NAIC)\cite{naic21}, all are recognized for their 
reliability in documenting catastrophic events and their associated economic and insured losses.

@@

\section{Discussion}
\label{sec:disc}

>>>>

\section{Data}
\label{sec:data}
To comprehend the impact of weather-related catastrophic events on property insurance pricing, we will begin by examining a dataset of 
billion-dollar disasters. This dataset provides crucial information on event frequency, financial cost, and other key parameters. Our 
data sources include the National Centers for Environmental Information (NCEI)\cite{ncei}, the Insurance Information Institute 
(III)\cite{iii}, Aon\cite{aon} and the National Association of Insurance Commissioners (NAIC)\cite{naic}, all are recognized for their 
reliability in documenting catastrophic events and their associated economic and insured losses.

@@

\section{Discussion}
\label{sec:disc}
The analysis reveals a statistically significant relationship between extreme weather disasters and homeowners insurance pricing. 
Results suggest that more frequent and severe events are associated with rising premiums, particularly for hurricanes and flooding 
perils. This comports with prior findings on the influence of catastrophic losses on insurance markets \cite{aon}.

However, there are limitations when looking at the data collected. Analytics could be better off using more granular, address-level 
premium data isolate local hazards. The model also fails to treat changes in exposures and vulnerabilities over time as risk factors
The risk has increased. Further research should aim to eliminate the impact of changing climate risk information from other luxury 
consumption measures.

Nonetheless, these findings highlight the interconnectedness of escalating extreme events and property insurance costs. As climate 
change exacerbates weather extremes, this could create affordability challenges for homeowners and threaten insurance market stability 
\cite{naic}. Along with mitigation to curb emissions, policy interventions like subsidized insurance, resilience incentives, and home 
hardening investments could help manage risk and facilitate affordable coverage \cite{kousky}. Climate risk modeling and risk-based 
pricing will also grow increasingly important for insurers to sustainably provide financial protection amid rising extremes.
